\section{Relevant Experience}

\begin{experience}{Deal Technologies}{
		\position{Full Stack Engineer}{2022}{\phantom{2022}}
}
Collaborated with three distinct clients to deliver tailored solutions.\\

\begin{enumerate}
  \item{\textit{B3 - Bolsa Brasil Balcão}\begin{contribs}
  \item Spearheaded the end-to-end development of a new, Unified Registry System for Brazil's national stock exchange, architecting a modern and efficient platform from the ground up.
  \item Engineered the system using Angular on the front-end and Java on the back-end, resulting in a 40\% reduction in system downtime and more than 2x the performance.
  \item The Unified Registry System is now the backbone of Brazil's only stock exchange, and is where companies and users manage and log vital changes and transactions.
\end{contribs}}
  \item{\textit{Veloe}\begin{contribs}
	\item{Maintained and expanded the codebase that powers the whole of Brazil's toll tags, ensuring its seamless operation for millions of users across the country.}
	\item{Developed new AI implementations to enhance the license plate recognition system, resulting in a 50\% increase in accuracy.}
\end{contribs}}
  \item{\textit{Banco BV}\begin{contribs}
	\item{Drove the creation of an innovative new app for solar panel financing and acquisition with the BVLab team, which is projected to increase new client acquisition by 15\% in the first year.}
	\item{Authored comprehensive documentation on development processes and challenges, establishing a knowledge base that is expected to accelerate future project timelines significantly.}
\end{contribs}}
\end{enumerate}
\end{experience}

\begin{experience}{360 Global Technology}{
		\position{Full Stack Engineer}{2021}{2022}
}
Developed my front and back-end skills on a variety of different projects.\\
\begin{contribs}
	\item{Developed and deployed a variety of web applications, including dynamic landing pages, high-traffic streaming platforms, and feature-rich e-commerce sites.}
	\item{Managed the complete project lifecycle, from initial planning and requirements gathering to final deployment on Linux servers, consistently delivering projects ahead of schedule.}
	\item{Enhanced performance by implementing modern web development technologies and frameworks like Node.js and React.js and cloud-based solutions like AWS and Azure.}
	\item{Built and integrated RESTful APIs to support seamless data flow between the front-end and back-end systems.}
\end{contribs}

\end{experience}

\begin{experience}[last]{Elisyum LTDA}{
		\position{Full Stack Engineer}{2020}{2021}
}
Gained experience working with a large company and of the inner workings of conventional financial operations.\\
\begin{contribs}
	\item{Architected and implemented a large-scale, interconnected e-commerce platform with a comprehensive administration dashboard, featuring advanced financial management and treasury systems.}
	\item{Developed a bespoke, first-party payment processing system from scratch, which successfully processed over \$500,000 in transactions within the first six months.}
	\item{Integrated multiple third-party services, enhancing the platform's functionality and providing a more robust user experience.}
	\item{Contributed to a 30\% increase in operational efficiency by automating key financial reporting processes within the administration dashboard.}
\end{contribs}

\end{experience}
