\section{Selected Projects}

\begin{experience}{Stock exchange management system}{
        \position{Unified Registry(CADU) - B3}{Sep 2024}{Jan 2025}
}
Gained experience working under a strict timetable and a regimented daily SCRUM/Kanban routine.

\begin{contribs}
	\item{Implemented industry-standard DRM and security protocols for protection of digital content.}
	\item{Developed AI for content recommendations based on user preferences.}
	\item{Implemented multiple profiles system for tailored recommendations, similar in funcionality to NETFLIX's.}
\end{contribs}
\end{experience}

\begin{experience}{Solar panel financing platform}{
        \position{BVLab - Banco BV}{Sep 2022}{Mar 2023}
}
Gained experience working with a large company and of the inner workings of conventional financial operations.

\begin{contribs}
	\item{Large interconnected project including store pages and administration dashboard with advanced finances management and treasury systems made from scratch.}
	\item{Implemented a custom first-party payment processing system.}
\end{contribs}
\end{experience}

\begin{experience}{Large-scale food distribution e-commerce}{
        \position{A2PFOOD}{Apr 2022}{Jul 2022}
}
Gained experience working with a large company and of the inner workings of conventional financial operations.

\begin{contribs}
	\item{Large interconnected project including store pages and administration dashboard with advanced finances management and treasury systems made from scratch.}
	\item{Implemented a custom first-party payment processing system.}
\end{contribs}
\end{experience}
